Brownian Dynein Model

### 2015-09-30 latex/derivation.tex
Simplify cartesian motor solutions. Next step: further simplification and verification.

We then expand $L_{n}$...

@@

>>>>

We then expand $L_{n}^2$...

@@

and $L_{f}^2$...

\begin{align}
  X_{nm} &= \frac{L_{s}}{L_{n}}\Bigg( \Big(\frac{L^2-2L_{t}L_{s}\cos(\Theta_{nm})+2L_{t}L_{s}\cos(\Theta_{fm})}{2L}\Big)\Big(\frac{2L_{s}^2-2L_{t}L_{s}\cos(\Theta_{nm})}{2L_{s}}\Big) \mp \\
  & \sqrt{L_{s}^2+L_{t}^2-2L_{t}L_{s}\cos(\Theta_{nm})-\bigg(\frac{L^2-2L_{t}L_{s}\cos(\Theta_{nm})+2L_{t}L_{s}\cos(\Theta_{fm})}{2L}\bigg)^2}\sqrt{L_{s}^2+L_{t}^2-2L_{t}L_{s}\cos(\Theta_{nm})-\bigg(\frac{2L_{s}^2-2L_{t}L_{s}\cos(\Theta_{nm})}{2L_{s}}\bigg)^2} \Bigg) \\
  Y_{nm} &= \frac{L_{s}}{L_{n}}\Bigg(\frac{2L_{s}^2-2L_{t}L_{s}\cos(\Theta_{nm})}{2L_{s}}\sqrt{L_{s}^2+L_{t}^2-2L_{t}L_{s}\cos(\Theta_{nm})-\bigg(\frac{L^2-2L_{t}L_{s}\cos(\Theta_{nm})+2L_{t}L_{s}\cos(\Theta_{fm})}{2L}\bigg)^2} \pm \\
  & \frac{L^2-2L_{t}L_{s}\cos(\Theta_{nm})+2L_{t}L_{s}\cos(\Theta_{fm})}{2L}\sqrt{L_{s}^2+L_{t}^2-2L_{t}L_{s}\cos(\Theta_{nm})-\bigg(\frac{2L_{s}^2+-2L_{t}L_{s}\cos(\Theta_{nm})}{2L_{s}}\bigg)^2} \Bigg) \\
\end{align}

We then do some simplification...

\begin{align}
  X_{nm} &= \frac{L_{s}}{L_{n}}\Bigg( \Big(\frac{L^2+2L_{t}L_{s}(\cos(\Theta_{fm})-\cos(\Theta_{nm}))}{2L}\Big)\Big(2L_{s}-L_{t}\cos(\Theta_{nm})\Big) \mp \\
  & \sqrt{L_{s}^2+L_{t}^2-2L_{t}L_{s}\cos(\Theta_{nm})-\bigg(\frac{L^2+2L_{t}L_{s}(\cos(\Theta_{fm})-\cos(\Theta_{nm}))}{2L}\bigg)^2}\sqrt{L_{t}^2-L_{t}^2\cos^2(\Theta_{nm})} \Bigg) \\
  Y_{nm} &= \frac{L_{s}}{L_{n}}\Bigg(L_{s}-L_{t}\cos(\Theta_{nm})\sqrt{L_{s}^2+L_{t}^2-2L_{t}L_{s}\cos(\Theta_{nm})-\bigg(\frac{L^2+2L_{t}L_{s}(\cos(\Theta_{fm})-\cos(\Theta_{nm}))}{2L}\bigg)^2} \pm \\
  & \frac{L^2+2L_{t}L_{s}(\cos(\Theta_{fm})-\cos(\Theta_{nm}))}{2L}\sqrt{L_{t}^2-L_{t}^2\cos^2(\Theta_{nm})} \Bigg) \\
\end{align}

And even more simplification...

\begin{align}
  X_{nm} &= \frac{L_{s}}{L_{n}}\Bigg( \Big(\frac{L^2+2L_{t}L_{s}(\cos(\Theta_{fm})-\cos(\Theta_{nm}))}{2L}\Big)\Big(2L_{s}-L_{t}\cos(\Theta_{nm})\Big) \mp \\
  & L_{t}\sin(\Theta_{nm})\sqrt{L_{s}^2+L_{t}^2-2L_{t}L_{s}\cos(\Theta_{nm})-\bigg(\frac{L^2+2L_{t}L_{s}(\cos(\Theta_{fm})-\cos(\Theta_{nm}))}{2L}\bigg)^2} \Bigg) \\
  Y_{nm} &= \frac{L_{s}}{L_{n}}\Bigg((L_{s}-L_{t}\cos(\Theta_{nm}))\sqrt{L_{s}^2+L_{t}^2-2L_{t}L_{s}\cos(\Theta_{nm})-\bigg(\frac{L^2+2L_{t}L_{s}(\cos(\Theta_{fm})-\cos(\Theta_{nm}))}{2L}\bigg)^2} \pm \\
  & \frac{L^2+2L_{t}L_{s}(\cos(\Theta_{fm})-\cos(\Theta_{nm}))}{2L}L_{t}\sin(\Theta_{nm}) \Bigg) \\
\end{align}
